Supplementary information

### 2021-09-28 _targets.Rmd
clean up

```{targets toy_globals, tar_globals = TRUE}
toy_growth_rates <- tibble(r = c(0, 0.1, 0.5, -0.1, -0.5))
```

@@

Thee pipeline can then be run using,

@@

>>>>

```{targets toy_globals, tar_globals = TRUE}
toy_growth_rates <- tibble(r = c(0, 0.1, 0.25, -0.1, -0.25))
```

@@

The pipeline can then be run using,

@@

Alternatively the pipeline can be explored interactively using this notebook.
